---
title: "How to use ridgereg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use ridgereg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

The `labbonus` package provides a `ridgereg` class for ridge linear regression in R. This vignette serves as a guide to understanding and using the main functions provided by the package.

# Installation

To install the `labbonus` package, use the following commands:


```{r install-labbonus-package, eval=FALSE}
devtools::install_github("qqyfly/732A94_Advanced_Programming_in_R_Lab_Bonus", build_vignettes = TRUE)
```

# Linear Regression with ridgereg

The core function in the `labbonus` package is `ridgereg` S3 class, which initializes a linear regression model with all the calculated values stored as a list.

This example demonstrates how to create a ridgereg object and how to use all the exported functions of this `ridgereg` S3 class.

## Load required libraries

In this step, we need to load the installed library `labbonus`. The code is showed below.

The required packages will be download and installed automatically.

```{r load-labbonus-package}
library(labbonus)
```

## Create a ridgereg object

Let's create a simple linear regression model using iris data set with the formula

```{r create-labbonus-object-normal}
ridgereg_mod <- ridgereg(Petal.Length ~ Species, data = iris, lambda = 1)
```

or you can also use qr to calculate a ridgereg object

```{r create-labbonus-object-qr}
ridgereg_mod <- ridgereg(Petal.Length ~ Species, data = iris, lambda = 1, qr = TRUE)
```


## Print a ridgereg object

This function use the pre created ridgereg object as a parameter, and print out some information of the regression model.

```{r print-labbonus-object}
print(ridgereg_mod)
```

## Get coef values of regression model

This function use the pre created ridgereg object as a parameter, and return the coef values of regression model.

```{r get-labbonus-object-coef}
coef(ridgereg_mod)
```

## Predict new values using model

This function use the pre created ridgereg object as a parameter, and return the coef values of regression model.

```{r predict_new_value}
predict(ridgereg_mod,x=c(1,2,3,4))
```

## Visualize Delay & Distance Relationship

```{r visualize}
visualize_airport_delays()
```

